\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=red,
    filecolor=magenta,      
    urlcolor=cyan,
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Image Processing for Analysis of Hand Drawn Multi-Loop Circuit Diagrams}


\author{\IEEEauthorblockN{Sara Jameel}
\IEEEauthorblockA{\textit{Habib University}\\
Karachi, Pakistan \\
sj03693@st.habib.edu.pk}
\and
\IEEEauthorblockN{Muhammad Shahrom Ali}
\IEEEauthorblockA{\textit{Habib University }\\
Karachi, Pakistan \\
ma03559@st.habib.edu.pk}
}

\maketitle

\begin{abstract}
Abstract Here
\end{abstract}

\begin{IEEEkeywords}
Circuit Analysis, Image Processing, Hand drawn circuits
\end{IEEEkeywords}

\section{\textbf{Introduction}}


\section{\textbf{Literature Review}}


% \subsection{Control Plane}


\section{\textbf{Methodology}}

% \subsection{Host}

% \subsection{Software-based switches}

% \subsection{Virtual ethernet links}

% \subsection{Python API}


\section{\textbf{Results}}

% \subsection{Implementing The VLAN Host Class}

% \subsection{Implementing The Network Topology}

% \subsection{Implementing The Command-line Interface}

\section{\textbf{Conclusion}}

\begin{thebibliography}{00}

\bibitem{hamza_azeem}
Larik, M., Ur Rehman, S., and Azeem, S., n.d. \textit{A Tool For Digitizing And Analyzing Hand Drawn Circuit Sketches.}

\bibitem{rabbani}
Mahdi Rabbani, Reza Khoshkangini, H.S. Nagendraswamy, Mauro Conti,
\textit{Hand Drawn Optical Circuit Recognition}, Procedia Computer Science,
Volume 84,
2016,
Pages 41-48,
ISSN 1877-0509,
\href{https://www.sciencedirect.com/science/article/pii/S1877050916300783}{Access Here}

\bibitem{}
S. K. Vasudevan, K. Venkatachalam, S. Anandaram and A. J. Memon, \textit{A Novel Method for Circuit Recognition Through Image Processing Techniques}, Asian Journal of Information Technology, vol. 15, no. 7, pp. 1146-1150, 2016. \href{https://www.scopus.com/inward/record.uri?eid=2-s2.0-84975519853&partnerID=40&md5=079e85950109992c1991a272f31fc35b}{Access Here}

\bibitem{}
L. Naika R, D. R and P. S, \textit{Handwritten Electric Circuit Diagram Recognition: An Approach Based on Finite State Machine}, International Journal of Machine Learning and Computing, vol. 9, no. 3, pp. 374-380, 2020.

\end{thebibliography}
\end{document}
